```{r}
ggplot(data = penguins) + geom_histogram(mapping = aes(x = flipper_length_mm))
```
```{r}
ggplot(mpg, aes(displ, hwy, colour = class)) + 
  geom_point()
```
ggplot is a function that takes in a data frame and then we add layers to it. The first layer is geom_histogram which is a histogram. The second layer is geom_point which is a scatterplot. The mapping argument is used to specify which variables are used for the x and y axis. The colour argument is used to specify which variable is used for the colour of the points. 

create ggplot bar chart
```{r}
ggplot(data = penguins) + geom_bar(mapping = aes(x = species))
```
```{r}
add color in ggplot bar chart # nolint
ggplot(data = penguins) + geom_bar(mapping = aes(x = species, fill = species))
```

explian above code

make letter z with ggplot

```{r}
ggplot(data = penguins) + geom_bar(mapping = aes(x = species, fill = species)) + 
  labs(x = "Species", y = "Count", fill = "Species")
```

```{r} 
ggplot(data = penguins) + geom_bar(mapping = aes(x = species, fill = species)) + 
  labs(x = "Species", y = "Count", fill = "Species")
```



